Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}

### 2020-08-26 main.tex
Added a couple of pending references in the encryption preliminaries section

\subsection{Security Notions}
The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}. The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{}. 
\begin{definition}
An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.

The formal security game for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
\end{definition}
Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{}. 
\begin{definition}
An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.

@@

\subsection{Paillier Encryption Scheme} \label{subsec:paillier_scheme}
The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme which bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA. Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $N=pq$. A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{}. The public key is defined by $(N, g)$ and secret key by $(p, q)$.

@@

                (N+1)^{(\omega^{(t)}_{j})}r_j^N\pmod{N^2},\,1\leq j\leq m

@@

                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N H(t)^{sk_i} \pmod{N^2}

@@

            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle\,,

>>>>

\subsection{Security Notions}
The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}. The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}. 
\begin{definition}
An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.

The formal security game for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
\end{definition}
Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. 
\begin{definition}
An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.

@@

\subsection{Paillier Encryption Scheme} \label{subsec:paillier_scheme}
The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme which bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA. Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $N=pq$. A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{katzIntroductionModernCryptography2008}. The public key is defined by $(N, g)$ and secret key by $(p, q)$.

@@

                (N+1)^{\omega^{(t)}_{j}}r_j^N\pmod{N^2},\,1\leq j\leq m

@@

                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N H(t)^{sk_i} \pmod{N^2}

@@

            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle
